Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework

### 2019-04-17 paper/main.tex
Adding section4 half

Precoding matrices obtained from the SVD of the wireless MIMO channel matrix can be utilized at the transmitter for optimum power allocation and lower BER\footnote{Bit Error Rate} transmissions.
However, a key step that enables this improved performance is feedback of these precoders to the transmitter from the receiver.
Since bit budget for such channel state information (CSI) feedback is limited, precoders need to be quantized effectively using with very few bits.
For a $N_T \times N_R$ MIMO system, this amounts to quantizing a $N_T \times N_R$ complex valued matrix.
This can be simplified by using the underlying manifold structure, and temporal/frequency correlations in the precoders.
In this work, we introduce a reservoir computing based framework for prediction of the new precoders by observing pastprecoders and utilizing temporal correlations.
Past methods have primarily exploited the nonlinear geometry endowed by the manifold structure to for precoder interpolation and prediction.
Here, this non-linear relationship is captured using the dynamical reservoir state as part of the training process of the reservoir.
Simulations reveal that this approach produces reduced quantization error, thereby resulting in lower BER as well as improved achievable rates when compared to earlier work.

@@

\section{Introduction}
\label{intro}
% Broad summary of your work, come to your problem definition.
In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ information vector onto an $N_T$-dimensional transmit vector that corresponds to the signal emanating out of the $N_T$ antennas of the transmitter.
The precoding matrix used to achieve the channel capacity using optimal power allocation is obtained using the SVD of the MIMO channel matrix \cite{love2008overview}.
The MIMO channel matrix is estimated at the receiver, and the transmitter has no a-priori knowledge of the same.
Therefore, to obtain the said benefits of SVD precoders, the receiver needs to quantize and feed back the precoders it estimates from the SVD of the MIMO channel matrix.
To honour the bit budget imposed by limited feedback CSI schemes, the quantization needs to be performed using very few bits.
Given the high dimensionality of the precoders (which form a $N_T \times N_R$ complex valued matrix, viz. $2\times N_T\times N_R$ real numbers), effective quantization with just a few bits poses a significant challenge.

% Elaborate on each point (what people have done before) lecunnas
Past work has used two inherent properties of the precoders to enable effective low-rate precoder feedback.
First, the precoders are not actually $2\times N_T\times N_R$ dimensional entities, and these have an underlying manifold structure that allows one to work with lower dimensions if one performs operations over the manifold directly.
Second, these precoders are correlated in both time and frequency.
Capturing temporal correlations allows the use off predictive quantization algorithms that improvement of the quantization error with time by effectively utilizing all information.
Exploiting frequency correlations permits the use of interpolation algorithms, which in turn reduce the feedback overhead in a single OFDM frame, by feeding back CSI information only for certain subcarriers, and interpolating over the others.
Despite the existence of the underlying manifold structure that possesses effective lower dimensions, most of the na{\"i}ve algorithms that predict and interpolate are limited in their effectiveness, owing to the inherent non-linear structure of the manifold.
Thus, combining these two properties, viz. the underlying manifold structure and temporal-frequency correlations, requires a generalization of such linear algorithms to the manifold under consideration, by exploiting the differential geometry of the manifold. Relevant past work in this direction has been \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,khaled2005quantized,krishnamachari2013geometry}.

% What is the way ahead
Manifold based approaches have provided significant performance benefits, given that they work with effective lower dimensions.
However, these approaches are difficult to implement and require some familiarity with manifold geometry for a complete grasp.
In this paper, we propose a reservoir computing based predictive quantizer to exploit the temporal correlations effectively.
The proposed scheme offers a cleaner solution to the predictive quantization problem, which brings about both ease of implementability, and improved performance as well, when compared to \cite{6891198}, which proposed a manifold based method of predictive quantization.

% How to we do this
Reservoir computing is a computational framework designed for sequential data processing.
Its design is inspired from several frameworks of recurrent neural networks \cite{jaeger2004harnessing}, including Liquid State Machines \cite{jalalvand2015real}.
A reservoir computing system maps the inputs to spatio-temporal patterns in a higher dimensional dynamical reservoir state.
The pattern analysis over these spatio-temporal patterns is performed by an output coupler that maps the higher dimensional reservoir state back to the output dimension that generally possesses lower dimensionality than the reservoir state.
% A important characteristic of reservoir computing is that while training, the input weights and the weights within the reservoir are not kept fixed and the weights of the output coupler are updated.
The key advantage of a reservoir computing based system is that it is extremely easy to train in comparison to its counterparts like Deep Neural Networks. CITATION NEEDED
The input features can be efficiently learnt using a simple learning algorithm, since the reservoir non-linearly transforms sequential inputs into a higher dimensional reservoir state.
Reservoir computing has been successfully used to solve problems like spoken digit recognition \cite{verstraeten2005isolated}, handwritten digit image recognition \cite{jalalvand2015real} and climate prediction \cite{pathak2017using}.
% Owing to the versatility of reservoir computing, it can deal with any sequential data in principle and hence further expansion of its application fields is widely expected.

Reservoir computing has also been applied to solve problems in the domain of wireless communications \cite{jaeger2004harnessing,mosleh2017brain,shafin2018realizing}.
\cite{jaeger2004harnessing} used reservoir computing framework to harness channel non-linearities in order for smarter channel equalization.
\cite{mosleh2017brain,shafin2018realizing} utilized this technique for OFDM symbol detection while accounting for channel and power amplifier non-linearities.
In our work, we utilize the reservoir computing framework to discover the underlying nonlinear relations between previously observed precoding matrices, in order to predict the next precoder in series.
Upon vectorizing the precoding matrices, this becomes analogous to time series prediction algorithms, for which the reservoir computing framework has been known to work effectively \cite{mosleh2017brain}.

\section{System Model}
\label{section2}
\noindent We consider a point-to-point MIMO-OFDM wireless system that
has $N_T$ transmit antennas and $N_R$ receive antennas.
The available bandwidth is divided into $N$ subcarriers, so that, individually for each subcarrier, the channel can be assumed to be flat fading.
The transmitter communicates an $N_s \times 1$ information data vector, where $N_s \leq \text{min}(N_T,N_R)$, and the $N_T \times N_s$ precoding matrix maps the $N_s \times 1$ information data vector onto the $N_T \times 1$ transmit vector emanating out of the transmitter.

In this discussion, we assume that $N_T > N_R$ and $N_s = N_R$.
Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the $N_R \times 1$ data stream received on the $i$-th subcarrier is denoted by:
\begin{equation}
\by_{i,t}=\bH^{H}_{i,t}\tilde{\bU}_{i,t}\bx_{i,t}+ \bw_{i,t}
\end{equation}
$\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ represents the precoding matrix, which is a function of quantized CSI fed back by the receiver, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_R \times 1}$ denotes the transmitted signal, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d. complex Gaussian noise with $\bw_{i,t} \sim \mathcal{N}_{\mathbb{C}}(0,N_0\bI_{N_R})$, $N_0$ being the noise variance.

@@

If an infinite bit budget is available for quantization, the transmitter can directly use the matrices obtained from SVD of $\bH^{H}_{i,t}$ as the precoder $\tilde{\bU}_{i,t}$.
In particular, if $\text{SVD}(\bH_{i,t}) = \bU_{i,t},\Sigma_{i,t}, \bV_{i,t}$, then $\tilde{\bU}_{i,t} = \bU_{i,t}$.
Notice that matrices $\bU_{i,t}$ reside on the Stiefel manifold $\text{St}(N_T,N_R)$, since the columns of $\bU_{i,t}$ form a set of $N_R$ orthogonal vectors in $N_T$ dimensions \cite{Gupt1905:Predictive,6891198}.
Given practical limitations, only limited feedback is available from the receiver, and the objective is to find a `reasonable' estimate of $\bU_{i,t}$, given by $\tilde{\bU}_{i,t}$ using the available feedback bits.

Algorithms similar to the Lloyd codebook algorithm have been studied for quantizing $\text{St}(N_T,N_R)$ \cite{6678348}.
However, this method treats precoders that are close to each other in time or frequency as independent, since it does not exploit any temporal/spectral correlations for quantization.
Predictive quantization algorithms \cite{Gupt1905:Predictive,6891198} can be utilized to reduce the quantization error with time by utilizing the available correlations.

We now discuss the basic mathematical model that is central to predictive quantization algorithms for precoding matrices.
Suppose that we predict the current precoding matrix based on the past $p$ observed precoding matrices, and hence $\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1}$ have been fed back and available at the transmitter.
By using a prediction algorithm  and by exploiting time correlations among precoders at $t-p,t-p+1,\ldots,t-2,t-1$ time instances, the transmitter can predict $\tilde{\bU}_{i,t}$ to be some $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)^p \to \text{St}(N_T,N_R)$ is a prediction function.
Now, since the transmitter already possesses a coarse estimate of $\tilde{\bU}_{i,t}$ given by $\bP_{i,t}$, the receiver just quantizes the local space of $\text{St}(N_T,N_R)$ nearby $\bP_{i,t}$ to facilitate the construction of a refined estimate of $\tilde{\bU}_{i,t}$ at the transmitter.
That is, the transmitter utilizes a quantization function $q_P:\text{St}(N_T,N_R) \times \mathbb{N} \to \text{St}(N_T,N_R)$, to obtain $\tilde{\bU}_{i,t} \gets q_P(\bP_{i,t},\text{fb}_{i,t})$, where $\text{fb}_{i,t} \in \{1,2\ldots2^{\mathcal{B}}\}$ is the feedback from the receiver for precoder at $i$-th subcarrier and $t$-th time instant, considering bit budget of $\mathcal{B}$ bits.
In \cite{Gupt1905:Predictive,6891198,6545375}, $\text{fb}_{i,t}$ denotes the codeword index for the codebook obtained for quantizing the local tangent space at $\bP_{i,t}$.

When using predictive quantization scheme, the quantization is performed on a smaller subspace when compared to the entire manifold in case of independent quantization.
Therefore, the quantization error is substantially lower as well.
However, quantization algorithms that are independent of these specific predictive structures are important for the initialization of these predictive quantization strategies.
Observe that predictive quantization algorithms for SVD precoders are typically the higher dimensional analogs of the well known approaches to reduce quantization error using linear prediction codes (LPCs) and Delta PCM.
In both LPCs and Delta PCM, quantization error can be reduced substantially using a linear predictor and quantizing the scalar difference between the predicted and observed value (innovation).
Analogous to this, for $\text{St}(N_T,N_R)$ quantization error is reduced by quantizing a subspace around the predicted value that is much smaller than the entire manifold.

In our work, we propose a reservoir computing based prediction framework that predicts the new precoders by utilizing  temporal correlations that are captured from past observed precoders ($f_P$).
We reuse the $q_P$ algorithm from \cite{Gupt1905:Predictive,6891198}.
However, by incorporating the $q_P$ in the prediction framework, as discussed in subsequent sections, the $f_P$ function also exploits correlations in $q_P$ (codebook locality correlations), along with temporal correlations.
Previous work \cite{Gupt1905:Predictive,6891198} has considered $f_P$ and $q_P$ to be independent of each other.
A detailed discussion on the reservoir computing based model for $f_P$ and $q_P$ is presented in Section \ref{section3}.
The proposed reservoir computing scheme is evaluated against the temporal predictive quantization scheme in \cite{6891198}, and the simulation results are discussed in Section \ref{section4}. Finally, Section \ref{section5} concludes and presents future lines of work.

@@

\section{Simulation Results}
\label{section4}
\subsection{Simulation setting considered}
\label{setting}
\noindent We compare the results of the proposed reservoir computing framework with the predictive quantization scheme presented in \cite{6891198}, which also captures the temporal correlations to enable reduced quantization error.
\subsection{Quantization Error, BER and Achievable Rate Results}
\label{res}
%Qtisn error with 1000 chan evols
%Qtisn error with 100 chan evols
%BER
%Achievable rat
\section{Conclusions and Future Work}
\label{section5}

>>>>

Precoding matrices obtained via SVD\footnote{Singular Value Decomposition} of the MIMO channel matrix can be utilized at the transmitter for optimum power allocation and lower BER\footnote{Bit Error Rate} transmissions. 
However, a key step enabling this improved performance is the feedback of these precoders to the transmitter from the receiver.
Considering the limited bit budget for such CSI\footnote{Channel State Information} feedback, the precoders need to be quantized with single digit number of bits.
For a $N_T \times N_R$\footnote{$N_T(R)$: Number of Transmit (Receive) Antennas} MIMO system, this amounts to quantizing a $N_T \times N_R$ complex valued matrix.
This odious task is helped by the presence of an underlying manifold structure, and temporal/frequency correlations in the precoders. 
In this work, we introduce a reservoir computing framework for the task of prediction of new precoders upon observation of past such precoders, by utilizing temporal correlations. 
This is a departure from existing methods which exploit the non linear geometry endowed by the manifold structure to perform the same.
Alternately, the non-linear relation is captured in our work via the dynamical reservoir state via the training process of the reservoir. 
Simulations reveal reduced quantization error, which results in lower BER as well as improved achievable rate, as compared to previous work.

@@

\section{Introduction}
\label{intro}
% Broad summary of your work, come to your problem definition. 
In MIMO wireless systems, precoding matrices are used for matrix transformation of $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ information vector onto the $N_T$-dimensional transmit vector, corresponding to the signal emanating out of the $N_T$ antennas of the transmitter.
The optimum precoding matrix, to achieve channel capacity via optimum power allocation is obtained via the SVD of the MIMO channel matrix. \cite{love2008overview}
The MIMO channel matrix is estimated at the receiver, and the transmitter has no a-priori knowledge of the same.
Hence, to avail the said benefits of SVD precoders, the receiver needs to quantize and feedback the precoders it obtains from SVD of the MIMO channel matrix.
To respect the bit budget imposed by limited feedback CSI schemes, the quantization needs to be performed only with a few single number of bits.
Given the high dimensionality of the precoders (which form a $N_T \times N_R$ complex valued matrix, viz. $2\times N_T\times N_R$ real numbers), effective quantization with just a few bits pose a significant challenge.

% Elaborate on each point (what people have done before) lecunnas
This challenge has been overcome in past work via two inherent properties of the precoders. 
Firstly, the precoders are not actually $2\times N_T\times N_R$ dimensional entities, and these actually have an underlying manifold structure which allows one to work with lower dimensions if one performs operations over the manifold directly.
Secondly, these precoders are correlated nicely along both time and frequency. 
Capturing temporal correlations allow for predictive quantization algorithms, which allow improvement of the quantization error with time.
Exploiting frequency correlations allow for various interpolation algorithms, which in turn reduce the feedback overhead in a single OFDM frame, by feeding back only for certain subcarriers, and interpolating over the others.
Although the underlying manifold structure allows one to work with effective lower dimensions, most of the naive linear algorithms to predict and interpolate don't work well here, owing to the inherent non-linear structure of the manifold.
Hence, combining these two properties, viz. the underlying manifold structure and temporal-frequency correlations, require generalization of such linear algorithms to the manifold under consideration, by exploiting the differential geometry of the manifold. Relevant past work in this direction has been \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,khaled2005quantized,krishnamachari2013geometry}.

% What is the way ahead
The manifold based approaches have provided significant performance benefits, given that they work with effective lower dimensions.
However, these approaches are difficult to implement and require some familiarity with manifold geometry for a complete grasp.
In this paper, we propose a reservoir computing based predictive quantizer to exploit the temporal correlations effectively.
The proposed scheme offers a cleaner solution to the predictive quantization problem, which brings about both ease of implementability, and improved performance as well, when compared to \cite{6891198}, which proposed a manifold based method of predictive quantization.

% How to we do this 
Reservoir computing is a computational framework designed for sequential data processing. 
It's design takes inspiration from several frameworks of recurrent neural networks \cite{jaeger2004harnessing} including Liquid State Machines \cite{jalalvand2015real}. 
A reservoir computing system maps the inputs to spatio-temporal patterns in higher dimensional dynamical reservoir state. 
The pattern analysis over these spatio-temporal patterns is performed by an output coupler which maps the higher dimensional reservoir state back to the output dimension, generally having lower dimensionality than reservoir state. 
% A important characteristic of reservoir computing is that while training, the input weights and the weights within the reservoir are not kept fixed and the weights of the output coupler are updated. 
The major advantage of reservoir computing system is that it’s extremely easy to train in comparison to its counterparts like Deep Neural Networks. 
The input features can be efficiently read out by a simple learning algorithm because the reservoir non-linearly transforms sequential inputs into the higher dimensional reservoir state. 
Reservoir computing has been successfully used to solve problems like spoken digit recognition \cite{verstraeten2005isolated}, handwritten digit image recognition \cite{jalalvand2015real} and climate prediction \cite{pathak2017using}.  
% Owing to the versatility of reservoir computing, it can deal with any sequential data in principle and hence further expansion of its application fields is widely expected.

Reservoir computing has also been applied to solve problems in the domain of wireless communications \cite{jaeger2004harnessing,mosleh2017brain,shafin2018realizing}. 
\cite{jaeger2004harnessing} used reservoir computing framework to harness channel non-linearities in order for smarter channel equalization.
\cite{mosleh2017brain,shafin2018realizing} utilized the same for OFDM symbol detection while tapping in channel, as well as power amplifier non-linearities.
In our work, we utilize the reservoir computing framework to discover the underlying non-linear relations between previously observed precoding matrices, in order to predict the next precoder in series. Upon vectorizing the precoding matrices, this becomes analogous to time series prediction algorithms, which the reservoir computing framework has been known to work really well for \cite{mosleh2017brain}.

%

\section{System Model}
\label{section2}
\noindent We consider a point-to-point MIMO-OFDM wireless system that
has $N_T$ transmit antennas and $N_R$ receive antennas. 
The available bandwidth is divided into $N$ subcarriers, so that individually for each subcarrier, the channel can be considered flat fading. 
The transmitter communicates an $N_s \times 1$ information data vector, where
$N_s \leq \text{min}(N_T,N_R)$, and the $N_T \times N_s$ precoding
matrix maps the $N_s \times 1$ information data vector onto the $N_T \times 1$ transmit vector emanating out of the transmitter.

In this discussion, we assume that $N_T > N_R$ and $N_s = N_R$. Keeping notations consistent with \cite{6891198,Gupt1905:Predictive}, the $N_R \times 1$ data stream received is denoted by:
\begin{equation}
\by_{i,t}=\bH^{H}_{i,t}\tilde{\bU}_{i,t}\bx_{i,t}+ \bw_{i,t}
\end{equation}
Here $\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the precoding matrix which is a function of quantized CSI fed back by the receiver, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_R \times 1}$ denotes the transmitted signal, all at the $i$-th subcarrier of the $t$-th OFDM frame, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d. complex Gaussian noise with $\bw_{i,t} \sim \mathcal{N}_{\mathbb{C}}(0,N_0\bI_{N_R})$, $N_0$ being the noise variance.

@@

Provided an infinite bit budget for quantization, the transmitter can directly use the matrices obtained from SVD of $\bH^{H}_{i,t}$ as precoder $\tilde{\bU}_{i,t}$.
In particular, if $\text{SVD}(\bH_{i,t}) = \bU_{i,t},\Sigma_{i,t}, \bV_{i,t}$, then $\tilde{\bU}_{i,t} = \bU_{i,t}$.
Notice that matrices $\bU_{i,t}$ reside on the Stiefel manifold $\text{St}(N_T,N_R)$, since the columns of $\bU_{i,t}$ form a set of $N_R$ orthogonal vectors in $N_T$ dimensions \cite{Gupt1905:Predictive,6891198}.  Given practical limitations, only limited feedback is available from the receiver, and the objective is to find a `reasonable' estimate of $\bU_{i,t}$, given by $\tilde{\bU}_{i,t}$ using the available feedback bits.

Algorithms similar to Lloyd codebook algorithm have been studied for quantizing $\text{St}(N_T,N_R)$ \cite{6678348}.
However, this method treats precoders close-by in time/frequency to each other as independent, since it doesn't exploit any temporal/spectral correlations for quantization. 
Predictive quantization algorithms \cite{Gupt1905:Predictive,6891198} can be utilized to reduce the quantization error with time by tapping in available correlations.

We now discuss the basic mathematical model central to predictive quantization algorithms for precoding matrices.
Consider that we predict based on past $p$ observed precoding matrices, and hence $\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1}$ have been fed back and available at the transmitter.
Using a prediction algorithm and exploiting time correlations among precoders at $t-p,t-p+1,\ldots,t-2,t-1$ time instances, the transmitter can predict $\tilde{\bU}_{i,t}$ to be some $\bP_{i,t}=f_P(\tilde{\bU}_{i,t-p},\tilde{\bU}_{i,t-p+1},\ldots,\tilde{\bU}_{i,t-2},\tilde{\bU}_{i,t-1})$, where $f_P: \text{St}(N_T,N_R)^p \to \text{St}(N_T,N_R)$ is a prediction function.
Now since the transmitter already knows a coarse estimate of $\tilde{\bU}_{i,t}$ given by $\bP_{i,t}$, the receiver just quantizes the local space of $\text{St}(N_T,N_R)$ nearby $\bP_{i,t}$ to enable a refined estimate of $\tilde{\bU}_{i,t}$ at the transmitter.
That is, the transmitter utilizes a quantization function $q_P:\text{St}(N_T,N_R) \times \mathbb{N} \to \text{St}(N_T,N_R)$, to obtain $\tilde{\bU}_{i,t} \gets q_P(\bP_{i,t},\text{fb}_{i,t})$, where $\text{fb}_{i,t} \in \{1,2\ldots2^{\mathcal{B}}\}$ is the feedback from the receiver for precoder at $i$-th subcarrier and $t$-th time instant, considering bit budget of $\mathcal{B}$ bits. 
In \cite{Gupt1905:Predictive,6891198,6545375}, $\text{fb}_{i,t}$ denotes the codeword index for the codebook obtained for quantizing the local tangent space at $\bP_{i,t}$.

Since using predictive quantization scheme, quantization is on a smaller subspace as compared to the entire manifold in case of independent quantization, the quantization error is substantially lower as well.
However, that being said, independent quantization algorithms are important for initialization the predictive quantization strategies.
Observe that, predictive quantization algorithms for SVD precoders are typically the higher dimensional analogs of the well known approaches to reduce quantization error using Linear Prediction Codes and Delta PCM.  
In both LPC and Delta PCM, quantization error is reduced substantially by using a linear predictor and quantizing the scalar difference between the predicted and observed value. 
Analogous to this, for $\text{St}(N_T,N_R)$ quantization error is reduced by quantizing a smaller subspace around predicted value, compared to the entire manifold.

In our work, we propose a reservoir computing based prediction framework, which predicts the new precoders by tapping the temporal correlations captured from past observed precoders ($f_P$). 
We reuse the $q_P$ algorithm from \cite{Gupt1905:Predictive,6891198}, however, by incorporating the $q_P$ in the prediction framework, as discussed in subsequent sections, the $f_P$ function also exploits correlations in $q_P$ (codebook locality correlations), along with temporal correlations. 
Previous work \cite{Gupt1905:Predictive,6891198} have $f_P$ and $q_P$ independent of each other.
The detailed discussion on reservoir computing based model for $f_P$ and $q_P$ is presented in Section \ref{section3}. 
The proposed reservoir computing scheme is evaluated against the temporal predictive quantization scheme in \cite{6891198}, and the simulation results are discussed in Section \ref{section4}. Finally, Section \ref{section5} concludes and presents future lines of work.

@@

\section{Simulation Results}
\label{section4}
\subsection{Simulation setting considered}
\label{setting}
\noindent We compare the results of the proposed reservoir computing framework with the predictive quantization scheme presented in \cite{6891198}, which captures the temporal correlations to enable reduced quantization error.
We simulate both our predictive quantization algorithms and the one presented in \cite{6891198} for the IEEE Pedestrian-A channel, with $N_T=4$, $N_R=2$. We simulated our algorithms by using the IT++ library through the Python wrapper py-itpp \cite{ViditPy}, with the channels being generated using Jake’s model for realistic simulations. Although in both our work and \cite{6891198}, only temporal correlations are exploited, we compare the BER, quantization error and logsum rate results for the MIMO-OFDM setting with number of subcarriers $N=64$, and evenly spaced $8$ feedback subcarriers, indexed from 0, viz. $\{0,9,\ldots,63\}$ ($\{9k, k \in \{0,1,\ldots,7\}\}$). The precoding matrices at non fedback subcarriers ($i\neq\{9k\}$) are estimated via the Cayley Interpolation method presented in \cite{Gupt1905:Predictive}. Feedback is available for $i=\{9k\}$ subcarriers (i.e. transmitter obtains $\text{fb}_{\{9k\},t}$) for predictive quantization. The setting is visually illustrated in Fig. BER, quantization error results have been simulated for $f_DT_s=3.5\times10^{-4}$, whereas for achievable rate we compare results for $f_DT_s=10^{-4},10^{-2},10^{-1}$. 
\newpage
\subsection{Quantization Error, BER and Achievable Rate Results}
Considering mitigation against randomly appearing drastic events in wireless channels, like sudden interferences, and dynamic environment, only 100 channel evolutions are considered for the simulations. 
\label{res}
%Qtisn error with 1000 chan evols
%Qtisn error with 100 chan evols
%BER
%Achievable rat
\section{Conclusions and Future Work}
\label{section5}
